diffEnrich: An \proglang{R} Package to Compare Functional Enrichment Between Two Experimentally-derived Groups of Genes by Connecting to the KEGG REST API

### 2019-11-22 jss-article-rnw-diffEnrich/article.Rnw
Added text for sec 2.3 in .Rnw

>>>>

<<diffEnrich, echo=TRUE>>=
## Perform differential enrichment
diff_enrich <- diffEnrich(list1_pe = list1_pe,
                          list2_pe = list2_pe,
                          method = 'none',
                          cutoff = 0.05)
@

The result of the \code{diffEnrich} call is a list object that
contains a data frame with the estimated odds ratio generated
by the Fisher's Exact test and the associated p-value. S3 generic
functions for \code{print} and \code{summary} are provided. The
\code{print} function prints the results table as a \code{tibble},
and the \code{summary} function returns the number of pathways
that reached statistical significance as well as their descriptions,
the number of genes used from the KEGG database, the KEGG species,
the number of pathways that were shared (i.e. had at least N gene
from each gene list present in the pathway based on what the user
chose for N in \code{pathEnrich}) between the gene lists and the
method used for multiple testing correction.

### 2019-11-22 jss-article-rnw-diffEnrich/article.tex
Added text for sec 2.3 in .Rnw

>>>>

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlcom{## Perform differential enrichment}
\hlstd{diff_enrich} \hlkwb{<-} \hlkwd{diffEnrich}\hlstd{(}\hlkwc{list1_pe} \hlstd{= list1_pe,}
                          \hlkwc{list2_pe} \hlstd{= list2_pe,}
                          \hlkwc{method} \hlstd{=} \hlstr{'none'}\hlstd{,}
                          \hlkwc{cutoff} \hlstd{=} \hlnum{0.05}\hlstd{)}
\end{alltt}
\end{kframe}
\end{knitrout}

The result of the \code{diffEnrich} call is a list object that
contains a data frame with the estimated odds ratio generated
by the Fisher's Exact test and the associated p-value. S3 generic
functions for \code{print} and \code{summary} are provided. The
\code{print} function prints the results table as a \code{tibble},
and the \code{summary} function returns the number of pathways
that reached statistical significance as well as their descriptions,
the number of genes used from the KEGG database, the KEGG species,
the number of pathways that were shared (i.e. had at least N gene
from each gene list present in the pathway based on what the user
chose for N in \code{pathEnrich}) between the gene lists and the
method used for multiple testing correction.
